---
title: "CENTREannotation"
author: "Sara Lopez Ruiz de Vargas"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{CENTRE AnnotationHub datasets}
  %\VignetteEngine{knitr::rmarkdown}
output: 
  BiocStyle::html_document
---

# CENTREannotation: An AnnotationHub package with the candidate cis regulatory elements for CENTRE

**CENTRE** is a package for Cell-type specific ENhancer Target pREdiction, that 
follows this workflow: 

`createPairs()` -> `computeGenericFeatures()` -> `computeCellTypeFeatures()` -> `centreClassification()`

The step `CENTRE::createPairs()` creates all possible enhancer-gene pairs at 500kb of
the input genes or enhancers. For this step CENTRE uses the [ENCODE SCREEN v3 enhancer annotation](https://screen.encodeproject.org) and the [GENCODE v40 gene annotation](https://www.gencodegenes.org/human/release_40.html)


All of the data in the CENTREannotation package can be accessed through AnnotationHub:

```{r, results='hide'}
library(AnnotationHub, quietly = TRUE)
```

```{r setup}
hub <- AnnotationHub()
ah <- query(hub, "CENTREannotation")
ah
```

The GENCODE database can now be accessed using `ah[["AH116730"]]` returs a CENTREannotgenedb object.
It can also be accessed using `CENTREannotation::CENTREannotgeneDb`

## The CENTREannotationgeneDb and CENTREannotationenhDb object

The objects  CENTREannotationgeneDb and CENTREannotationenhDb  represent the GENCODE
and ENCODE databases respectively
```{r, results='hide'}
CENTREannotation::CENTREannotgeneDb
CENTREannotation::CENTREannotenhDb
```

CENTREannotgeneDb contains:
- `gencode`: GENCODE v40 gene annotation table
- `metadata`: metadata for the AnnotationHub

CENTREannotenhDb contains:
- `ccres`: ENCODE SCREEN v3 candidate cis regulatory elements
- `metadata`: metadata for the AnnotationHub

The database can be used as follows: 
```{r}
conn <- RSQLite::dbConnect(CENTREannotation::CENTREannotgeneDb@conn)
RSQLite::dbGetQuery(conn, "SELECT * from metadata")
RSQLite::dbDisconnect(conn) # don't forget to disconnect
```

