---
title: "CENTREannotation"
author: "Sara Lopez Ruiz de Vargas"
date: "`r doc_date()`"
vignette: >
  %\VignetteIndexEntry{CENTRE AnnotationHub datasets}
  %\VignetteEngine{knitr::rmarkdown}
output: 
  BiocStyle::html_document
---

# CENTREannotation: An AnnotationHub package with the ENCODE cCREs V3 and 
GENCODE basic gene annotation v40 for the CENTRE package

**CENTRE** is a package for Cell-type specific ENhancer Target pREdiction, that 
follows this workflow: 

`createPairs()` -> `computeGenericFeatures()` -> `computeCellTypeFeatures()` 
-> `centreClassification()`

The step `CENTRE::createPairs()` creates all possible enhancer-gene pairs at 
500kb of the input genes or enhancers. For this step CENTRE uses the 
[ENCODE SCREEN v3 enhancer annotation](https://screen.encodeproject.org) and the
[GENCODE v40 gene annotation](https://www.gencodegenes.org/human/release_40.html)


All of the data in the CENTREannotation package can be accessed through 
AnnotationHub:

```{r load AnnotationHub, results='hide'}
library(AnnotationHub, quietly = TRUE)
```

```{r setup}
hub <- AnnotationHub()
ah <- query(hub, "CENTREannotation")
ah
```

The GENCODE database can be accessed using `ah[["AH116730"]]` and returns a 
CENTREannotgenedb object. It can also be accessed using 
`CENTREannotgeneDb`

## The CENTREannotationgeneDb and CENTREannotationenhDb object

The objects  CENTREannotgeneDb and CENTREannotenhDb  represent the GENCODE
and ENCODE databases respectively
```{r CENTREannotDb}
library(CENTREannotation)
CENTREannotgeneDb
CENTREannotenhDb
```

CENTREannotgeneDb contains:

- `gencode`: GENCODE v40 gene annotation table
- `metadata`: metadata for the AnnotationHub

CENTREannotenhDb contains:

- `ccres`: ENCODE SCREEN v3 candidate cis regulatory elements
- `metadata`: metadata for the AnnotationHub

The database can be used as follows:

- `tables()`: shows all the tables and columns in the database
- `fetch_data()`: interface to select data from the database (see man pages) 

```{r use CENTREannotDb}
tables(CENTREannotenhDb)
res <- fetch_data(CENTREannotenhDb,
    columns = c("enhancer_id", "start"),
    entries = c("EH38E1519134", "EH38E1519132"),
    column_filter = "enhancer_id"
)
```

```{r sessionInfo}
sessionInfo()
```
